Towards an Ecological Trait-data Standard - Appendix A

### 2018-05-28 manuscript/appendix_A.Rmd
fix appendix A author order

---
title: "Towards an Ecological Trait-data Standard - Appendix A"
author:
- name: Florian D. Schneider \footnotemark[1] \footnotemark[2] \footnotemark[3]
- name: David Fichtmüller \footnotemark[5]
- name: Anton Güntsch \footnotemark[5]
- name: Malte Jochum \footnotemark[4]
- name: Birgitta König-Ries\footnotemark[6]
- name: Gaetane Le Provost \footnotemark[3]
- name: Pete Manning \footnotemark[3]
- name: Andreas Ostrowski \footnotemark[5]
- name: Caterina Penone \footnotemark[4]
- name: Nadja K. Simons \footnotemark[7]
fontsize: 12pt
geometry: margin=0.5in
classoption: landscape
output:
  pdf_document:
    fig_caption: yes
    fig_crop: no
    keep_tex: yes
    template: pretty.template
  html_document:
    fig_caption: yes
    fig_width: 4
    highlight: null
    keep_md: yes
    theme: united
  word_document:
    fig_caption: yes
    fig_width: 6
---

@@

\footnotetext[1]{Corresponding author: florian.dirk.schneider@gmail.com}
\footnotetext[2]{Institute of Linguistics and Literary Studies, Technische Universität Darmstadt, Darmstadt, Germany}
\footnotetext[3]{Senckenberg Biodiversity and Climate Research Centre (BiK-F) Frankfurt am Main, Germany}
\footnotetext[4]{Institute of Plant Sciences, University of Bern, Bern, Switzerland}
\footnotetext[5]{Botanic Garden and Botanical Museum Berlin, Freie Universität Berlin, Berlin, Germany}
\footnotetext[6]{Department of Mathematics and Computer Science, Friedrich-Schiller-Universität Jena, Jena, Germany}
\footnotetext[7]{Department for Ecology and Ecosystem Management, Center for Life and Food Sciences Weihenstephan, Technische Universität München, Freising, Germany}

@@

>>>>

---
title: "Towards an Ecological Trait-data Standard - Appendix A"
author:
- name: Florian D. Schneider \footnotemark[1] \footnotemark[2] \footnotemark[3]
- name: Malte Jochum \footnotemark[4]
- name: Gaëtane Le Provost \footnotemark[3]
- name: Andreas Ostrowski \footnotemark[6]
- name: Caterina Penone \footnotemark[4]
- name: David Fichtmüller \footnotemark[5]
- name: Martin Gossner \footnotemark[8]
- name: Anton Güntsch \footnotemark[5]
- name: Birgitta König-Ries\footnotemark[6]
- name: Pete Manning \footnotemark[3]
- name: Nadja K. Simons \footnotemark[7]
fontsize: 12pt
geometry: margin=0.5in
classoption: landscape
output:
  pdf_document:
    fig_caption: yes
    fig_crop: no
    keep_tex: yes
    template: pretty.template
  html_document:
    fig_caption: yes
    fig_width: 4
    highlight: null
    keep_md: yes
    theme: united
  word_document:
    fig_caption: yes
    fig_width: 6
---

@@

\footnotetext[1]{Corresponding author: florian.dirk.schneider@gmail.com}
\footnotetext[2]{Institute of Linguistics and Literary Studies, Technische Universität Darmstadt, Darmstadt, Germany}
\footnotetext[3]{Senckenberg Biodiversity and Climate Research Centre (BiK-F) Frankfurt am Main, Germany}
\footnotetext[4]{Institute of Plant Sciences, University of Bern, Bern, Switzerland}
\footnotetext[5]{Botanic Garden and Botanical Museum Berlin, Freie Universität Berlin, Berlin, Germany}
\footnotetext[6]{Department of Mathematics and Computer Science, Friedrich-Schiller-Universität Jena, Jena, Germany}
\footnotetext[8]{Forest Entomology, Swiss Federal Research Institute WSL, Birmensdorf, Switzerland} <!--  Zürcherstrasse 111, CH-8903 -->
\footnotetext[7]{Chair for Terrestrial Ecology, Department of Ecology and Ecosystemmanagement,
Technische Universität München, Freising, Germany}

@@

\renewcommand{\thetable}{A\arabic{table}}
